%-------------------------
% Resume in Latex
% Author : David Goldstein
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{0pt}}
  }
}

\newcommand{\resumeSubItemWithoutTitle}[1]{
  \item\small{
    \textbf{#1}
  }
}

\newcommand{\resumeItemSub}[2]{
  \item\small{
    {#1}{: #2 \vspace{4pt}}
  }
}

\newcommand{\resumeItemNoColon}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{0pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemNoColon}[1]{\resumeItemNoColon{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  {\Large David Goldstein} \\ \\
  \href{mailto:dgoldstein01@gmail.com}{dgoldstein01@gmail.com}\\
  {617-543-0274} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Macalester College}{Saint Paul, MN}
      {Bachelor of Arts; Majors: Computer Science, Arabic, International Studies; GPA: 3.80}{Sept. 2012 -- May 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Target}{Minneapolis, MN}
      {Lead Software Engineer}{October 2021 - Present}
      \resumeItemListStart
        \resumeSubItemWithoutTitle{Developer Tooling}
        \resumeItemListStart
          \resumeItemSub{Github Actions}{Design and implement common VM architecture running Github Actions workers across GCP, VMWare, and Target's datacenter.}
          \resumeItemSub{Write Ahead Log KV}{Spearhead developement and architecture of Redis-driven Secret Provider for store workloads, now used in all 2000 stores and in HQ.}
          \resumeItemSub{Sidecar Monitoring and Obserability}{Drive initiative to rewrite sidecar tooling to support both GKE and Open Container runtimes, used in 100k+ workloads across Target's Datacenter and stores.}
        \resumeItemListEnd
        \resumeSubItemWithoutTitle{Virtual Machine Management}
        \resumeItemListStart
          \resumeItemSub{Persistent Disks}{Design and implement architecture to support local and network storage in support of Target Kuburnetes Engine.}
          \resumeItemSub{Placement Engine}{Redesign and optimize placement engine for VMs across Target's datacenter taking into account anti-affinity rules, resource availability, and user-driven constraints.}
        \resumeItemListEnd
        \resumeSubItemWithoutTitle{Hybrid Cloud}
        \resumeItemListStart
          \resumeItemSub{Compute Platform}{Lead Hybrid Cloud efforts to interface multiple compute providers (GCP, VMWare, internal Target) with one common API for use across Target.}
          \resumeItemSub{Workflow Management}{Architect and implement workflow orchestrator to significantly reduce complexity in management and debugging of operations across Cloud Providers.}
          \resumeItemSub{Open Policy Agent}{Drive and implement Target's enterprise-level OPA policies and rules from the ground up.}
        \resumeItemListEnd
      \resumeItemListEnd

    \resumeSubheading
      {Greymatter.io}{Washington, DC}
      {Lead Software Engineer}{May 2019 - October 2021}
      \resumeItemListStart

        \resumeSubItemWithoutTitle{Service Mesh}
        \resumeItemListStart
          \resumeItemSub{Authorization}{Drive architecture for zero-trust authentication and authorization at the L4 and L7 layers across Government and Commercial spaces.}
          \resumeItemSub{Machine Identity}{Core developer on integrating Spiffe/Spire as an out of the box machine-identity provider in distributed service meshes.}
          \resumeItemSub{Open Policy Agent}{Lead development on enabling OPA authorization for external OIDC providers in Hybrid Cloud evironments.}
          \resumeItemSub{Monitoring and Obserability}{Implement distributed metrics and alerting schemas for service meshes with 20k+ workloads.}
          \resumeItemSub{Customer Relations}{Serve as a primary techincal contact for the Department of Homeland Security, US Southern Command, and the Defense Intelligence Agency to intstall, operate, and upgrade Service Meshes.}
        \resumeItemListEnd



%        \resumeItem{Keycloak}
%          {Plan and lead development for OIDC integration for enterprises with 1,000+ applications}
%        \resumeItem{Object Drive}
%          {Lead a team of four developers on object-storage platform with 20,000+ users}
%        \resumeItem{Covidapihub.io}
%          {Lead a team of five to develop and deploy website hosting covid-19 data}
%        \resumeItem{API Development}
%          {Developed RESTful APIs used in leading service mesh framework}
%        \resumeItem{Observability}
%          {Develop metric system for measuring API performance in distributed environments}
%        \resumeItem{Kubernetes}
%          {Build, test, and deploy customer environments into AWS, Azure, and Openshift}
      \resumeItemListEnd

    \resumeSubheading
      {Defense Intelligence Agency}{Washington, DC}
      {Software Engineer}{Sept. 2016 - May 2017}
      \resumeItemListStart
     \resumeItem{Brief}
          {Develop end-to-end military capacity planning application for military leaders, including DIA senior leadership and the Joint Chiefs of Staff.}
     \resumeItem{Research}
          {Develop and perform database migrations and updates for highly sensitive data.}
      \resumeItemListEnd

    \resumeSubheading
      {National Intelligence University - School of Science and Technology}{Washington, DC}
      {Intern}{Summer 2016}
      \resumeItemListStart
        \resumeItem{Research}
          {Report on scientific advancements for the creation of US foreign policy.}
        \resumeItem{Administration}
          {Assist professors in management of course schedule and classroom.}
      \resumeItemListEnd

    \resumeSubheading
      {US Department of State - Bureau of Populations, Migration, and Refugees}{Washington, DC}
      {Intern}{Summer 2015}
      \resumeItemListStart
        \resumeItem{Research}
          {Report on key foreign-policy issues relating to migration in the Middle East.}
        \resumeItem{Administration}
          {Take meeting notes for high-level US Government meetings, send memos, assist in document production.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------QUALIFICATIONS------------
\section{Qualifications}
  \resumeSubHeadingListStart
    \resumeSubItem{CSM}
      {Certified Scrum Master with Scrum Alliance (2021)}
    \resumeSubItem{Top Secret-SCI}
      {Government clearance (2018)}
  \resumeSubHeadingListEnd

  
\section{Hobbies}
    \resumeSubHeadingListStart
        \resumeSubItemNoColon{Trail running, canoeing, XC Skiing}
    \resumeSubHeadingListEnd
\end{document}